\Title

### 2020-02-18 manuscript/manuscript.tex
Write description of synthetic model and surveys

@@

Our goal is to to compare the performance of all source distributions from
Table~\ref{tab:source-distributions} when predicting harmonic field data using
the equivalent layer technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on two
different set of observation points that we will call \emph{synthetic surveys}:
a ground and an airborne survey.
Its effect have also been computed on a regular grid at a constant height which
we will use as the \emph{target} values of the harmonic field.
Then the data from each synthetic survey is interpolated on the same grid
points as the \emph{target} grid using each source
distribution with different sets of parameters.
Each prediction is then scored against the \emph{target} grid and keep the one
that achieves the highest score.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

@@

The synthetic model is made out of 64 prisms distributed on a region of
\SI{100}{\km}$\times$\SI{100}{\km} between \SI{10}{\km} deep and the zero
height plane.
Density of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The gravitational effect of the synthetic model has been computed on a regular
grid of 56$\times$57 points with a spacing of \SI{2}{\km} located
\SI{2000}{\m} above the zero height plane (Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

@@

Create synthetic surveys to produce observation points.
In order to compare each source layout under very different set of observation
points we create a ground and an airborne synthetic surveys.
We selected a portion of the Southern Africa Gravity Data obtained by Dr. R.J.
Kleywegt et al.\ and made available through the NOAA website
(\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}) for creating
a synthetic ground survey.
We selected a portion of the Great Britain Aeromagnetic Survey acquired by
Hunting Geology and Geophysics Ltd and Canadian Aeroservices Ltd between 1955
and 1965 and made available by the
\href{
    https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html
    }{
    British Geological Survey (BGS)
}
, for creating a synthetic airborne survey.

The gravitation effect of the synthetic model has been computed on both surveys
and added Gaussian noise (standard deviation of 1mGal) to simulate acquisition
errors.

@@

%Describe the target grid. Show target grid figure.
%Describe the parameters used for each source distribution, how do we score
%each interpolation.
%Describe the Harmonica implementation of the EQL.
%Show results.

@@

>>>>

% Define special units
\DeclareSIUnit\mgal{\milli Gal}

@@

Our goal is to to compare the performance of all source distributions from
Table~\ref{tab:source-distributions} when predicting harmonic field data using
the equivalent layer technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on
a regular grid (\emph{target} grid) at a constant height and on two different
set of observation points that we will call \emph{synthetic surveys}: a ground
and an airborne survey.
The data from each synthetic survey is interpolated on the points of the
\emph{target} grid.
The interpolations are carried out using each source distribution and combining
different parameter values for each distribution.
Each prediction is then scored against the \emph{target} grid.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

@@

The synthetic model is made out of 64 prisms distributed on a region of
\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
height plane.
Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of 56$\times$57 points with a spacing
of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

@@

In order to compare the predictive capabilities of each source distribution
under on different surveys, we created a ground and an airborne \emph{synthetic
surveys}.
For creating the synthetic ground survey we selected a portion of the Southern
Africa Gravity Data available through the
\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
For the airborne survey we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made available by the
\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
British Geological Survey (BGS)
}.

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
The ground survey is composed by 963 observation points distributed at heights
ranging between \SI{0}{\m} and \SI{2052}{\m}
(Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has 5673 points at heights between \SI{359}{\m} and
\SI{1255}{\m}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
to the effect of the synthetic model to simulate acquisition errors.
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Synthetic airborne survey.
        (a)~Location of observation points.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
        Based upon the Great Britain aeromagnetic data, with the permission of
        the British Geological Survey.
    }
    \label{fig:synthetic-airborne-survey}
\end{figure}

@@

%Describe the parameters used for each source distribution, how do we score
%each interpolation.
%Show results.

@@

The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
$\textcopyright$UKRI\@.
All rights Reserved.
